%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage[numbers]{natbib}
\usepackage{bibentry}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNew}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheadingProject}[3] {
  \vspace{-1pt}\item
    \textbf{#1} (\textnormal{\href{#2}{#2}}): #3
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingNew}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
      \multicolumn{2}{l}{\textnormal{\small #5}} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingGradSchool}[6]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
      \multicolumn{2}{l}{\textnormal{\small #5}} \\
      \multicolumn{2}{l}{\textnormal{\small #6}} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
  
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\bibliographystyle{apalike_new}
\nobibliography{peveler}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://mpeveler.com/}{\Large Matthew Peveler}} & \href{mailto:matt.peveler@gmail.com}{matt.peveler@gmail.com}\\
  \href{https://mpeveler.com/}{https://mpeveler.com} & RR 1 Box 52, Warren, VT 05674 \\
  \href{https://github.com/MasterOdin}{https://github.com/MasterOdin} & (201) 478-3065
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingGradSchool
      {Rensselaer Polytechnic Institute}{Troy, NY}
      {Ph.D., Computer Science}{Nov 2020}
      %{Teaching Assistant: Fall 2013 - Spring 2015; Research Assistant: Fall 2015 - Fall 2020}
      {Thesis: Building Cognitive and Immersive Systems: Architecture, Implementation, and Formalization}
      {Advisor: Selmer Bringsjord}
    \resumeSubheadingNew
      {The College of New Jersey}{Ewing, NJ}
      {Bachelor of Science, Computer Science}{May. 2013}
      {Member of Upsilon Pi Epsilon, International Honor Society for Computing Sciences}
  \resumeSubHeadingListEnd

%-----------PUBLICATIONS---------------
\section*{Publications}
  \begin{itemize}
    \item \bibentry{yamamoto_category_2022}
    \item \bibentry{yamamoto_thematic_2021}
    \item \bibentry{kurosu_virtual_2020}
    \item \bibentry{peveler_browser_2020}
    \item \bibentry{chabot_collaborative_2020}
    \item \bibentry{divekar_humaine_2020}
    \item \bibentry{maicus_autograding_2020}
    \item \bibentry{govindarajulu_quantified_2019}
    \item \bibentry{briggs_multimodal_2019}
    \item \bibentry{peveler_reagent:_2019}
    \item \bibentry{kurosu_translating_2019}
    \item \bibentry{maicus_autograding_2019}
  	\item \bibentry{peveler_comparing_2019}
  	\item \bibentry{briggs_enabling_2019}
    \item \bibentry{divekar2018}
  	\item \bibentry{peveler2018acs}
    \item \bibentry{peveler2018icres}
    \item \bibentry{bringsjord2018_tai}
    \item \bibentry{govindarajulu2017icres}
    \item \bibentry{ied2016}
    \item \bibentry{mbr2015}
  \end{itemize}\vspace{-5pt}

%-----------PATENT APPLICATIONS--------------
\section{Patents}
  \begin{itemize}
      \item \bibentry{kephart_patent_2022}
      \item \bibentry{kephart_patent_2022_02}
  \end{itemize}
  
%-----------PRESENTATIONS--------------
\section{Presentations}
  \begin{itemize}
  	\item \bibentry{peveler2018_rpi}
  	\item \bibentry{sigcse2018-demo}
    \item \bibentry{rpi2017}
    \item \bibentry{sigcse2017-demo}
  \end{itemize}
  
%-----------POSTERS---------------------
\section{Posters}
  \begin{itemize}
    \item \bibentry{allen_metrics_2022}
    \item \bibentry{peveler_automated_2020}
    \item \bibentry{maicus_random_2020}
    \item \bibentry{peveler_lichen:_2019}
    \item \bibentry{aikens_facilitating_2019}
  	\item \bibentry{cislposter2018}
  	\item \bibentry{peveler2018sigcse_poster}
  	\item \bibentry{breese2018-poster}
    \item \bibentry{cisl-ibm-colloquium-poster2017}
    \item \bibentry{sigcse2017}
    \item \bibentry{cisl-ibm-colloquium-poster2016}
    \item \bibentry{sigcse2016}
    \item \bibentry{cislposter2015}
  \end{itemize}
  
%-----------RESEARCH-------------------
\section{Research Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Cognitive and Immersive Systems Laboratory at RPI}{Troy, NY}
      {Research Assistant}{Fall 2016 - Fall 2020}
        \resumeItemListStart
          \resumeItemNew{Conducted research for resolution of intents and entities from multi-modal contexts.}
          \resumeItemNew{Integrated different spatial context systems for gestural input to large-scale environments.}
          \resumeItemNew{Acted as technology liaison between RPI and IBM labs.}
          \resumeItemNew{Developed modules written in Node.js, and Python utilizing MongoDB, PostgreSQL, RabbitMQ, and Redis.}
          \resumeItemNew{Implemented usage of the formal logic and reasoner to handle theory of mind reasoning of agents.}
          \resumeItemNew{Created of Cognitive Polygon Framework for definition of tasks and cognitive agents in Blockworld-esque worlds.}
          \resumeItemNew{Developed and created modular framework for building ``Cognitive and Immersive Systems''.}
          \resumeItemNew{Formalized intelligent room behavior for use in plan and goal recognition algorithms.}
          \resumeItemNew{Developed collaborative in-person technologies for intelligence analysis.}
        \resumeItemListEnd

    \resumeSubheading
      {IBM - Brasil}{Rio de Janeiro, Brasil}
      {Pesquisador / Cientista - Junior (Junior Researcher)}{September 2019 -- December 2019}
      \resumeItemListStart
        \resumeItemNew{Developed a new digital sticky note tool for in-person design thinking meetings.}
        \resumeItemNew{Created a multi-user pointing system utilizing cellphone sensors for large-scale wall displays.}
        \resumeItemNew{Investigated camera-based approach for interacting with large-scale wall displays using transparent markers and multiplexing.}
        \resumeItemNew{Created and ran several user studies judging effectiveness of designed interfaces based on NASA Task Load Index.}
        \resumeItemNew{Contributed 33 patches to the IBM Watson Node.js SDK libraries.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {PopSQL}{Remote}
      {Software Engineer}{Nov 2020 - Present}
      \resumeItemListStart
        \resumeItemNew{Worked across the entire stack (Ruby on backend, TypeScript/React for frontend) to deliver new features and fix bugs.}
        \resumeItemNew{Helped architect new system to handle cloud database connections and streamed queries to reduce execution time and memory overhead.}
        \resumeItemNew{Helped develop various internal practices and procedures around developing the codebase.}
        \resumeItemNew{Improved various front-end efficency bottlenecks through algorithmic analysis.}
        \resumeItemNew{Worked on developing new and improving existing database adapters.}
        \resumeItemNew{Developed prototype dbt integration for the core product.}
        \resumeItemNew{Helped manage underlying infrastructure as defined through Terraform.}
      \resumeItemListEnd
        
    \resumeSubheading
      {Rensselaer Polytechnic Institute}{Troy, NY}
      {Teaching Assistant}{Fall 2013 -- Spring 2015}
      \resumeItemListStart
        \resumeItemNew{Ran labs and held office hours for Computer Science I.}
        \resumeItemNew{Acted as head TA for professor from Fall 2014 to Spring 2015.}
        \resumeItemNew{As head TA, helped professor manage other TAs, setup submission and grading for HWs, labs, and tests, dealt with cheaters, and other miscellaneous tasks.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Pitney Bowes}{Troy, NY}
      {Software Development Intern}{June 2014 -- Dec 2015}
      \resumeItemListStart
        \resumeItemNew{Worked on fixing bugs and improving testing efforts of the Location Intelligence module of Spectrum Spatial.}
        \resumeItemNew{Researched porting XML based test suites to native JUnit test suites.}
        % Rewrote the testing framework so that instead of test suites per data provider, use
        % paramerized test suites for each data provider to run it. Extensions allowed hooking
        % into each step of the test sequence for initializing and setting up and closing data
        % providers to prevent leaks
        \resumeItemNew{Created JUnit extensions for parametrized testing to simplify adding new data providers for testing.}
        \resumeItemNew{Implemented 9 functions to Spectrum Spatial's SQL dialect.}
      \resumeItemListEnd

    %\resumeSubheading
    %  {Media Technology Support Service at TCNJ}{Ewing, NJ}
    %  {User Support}{May 2011 ‐- Jul 2013}
    %  \resumeItemListStart
    %  	\resumeItemNew{Assist teachers with any issues they have with media technology.}
    %    \resumeItemNew{Diagnose and troubleshoot problems in media equipped classrooms.}
    %    \resumeItemNew{Deliver and set up media technology for professors.}
    %  \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Open Source Projects}
  \resumeSubHeadingListStart
    \resumeSubheadingProject{Submitty}{https://submitty.org}{Assignment submission and auto-grading server for Computer Science written using mix of PHP, Python, Bash, and C++.}
    \resumeSubheadingProject{phinx}{https://github.com/cakephp/phinx}{Framework agnostic database migration software written in PHP.}
    \resumeSubheadingProject{asciidoc-py}{https://github.com/asciidoc-py/asciidoc-py}{Python client for parsing AsciiDoc files into HTML and DocBook.}
    \resumeSubheadingProject{BishopCAIS}{https://github.com/bishopcais}{Modular framework for building "Cognitive and Immersive Systems", written in TypeScript and Python.}
    \resumeSubheadingProject{Slate}{https://github.com/slatedocs/slate}{Static API site generator written in Ruby, HTML, and JavaScript.}
    \resumeSubheadingProject{pypdf}{https://github.com/py-pdf/pypdf}{Pure python library for manipulating PDFs.}
    \resumeSubheadingProject{sqlectron}{https://github.com/sqlectron/sqlectron-gui}{Desktop SQL client written using TypeScript, React, and Electron.}
    \resumeSubheadingProject{HUMAINE}{https://github.com/humaine-anac}{Competition framework written in Node for running multi-agent negotiation against a human.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------

\end{document}